CTest Integration of Sikuli Automated GUI Testing

### 2011-06-17 Documentation/Article.tex
some more edits

GUI testing is a key aspect of software development. Having a well defined testing protocol is very
important in maintaining a productive flow, especially on the eve of a new release.  As the software becomes 
more complex, testing each feature can be immensely time consuming.  
We collected a list of over 400 different GUI tests which
involved endlessly repetitive clicking and checking.  This task took around 5 hours to complete each time a new release was ready.
And debugging would push release dates back days or even weeks.  We decided to tackle this problem by utilizing a new
scripting language called Sikuli that can automate any visual operation.  In this way we could write scripts to automate the GUI testing.
This cut the time to complete each test drastically.  Furthermore, we have integrated the automated tests with CTest.  Therefore we will be able to
run the collection of tests every night and find bugs as they arise instead of the night before a new release.  As a result,
the rate of new releases increased drastically.

@@

% Feel free to change section titles
\subsection{What is sikuli?}

@@

\subsection{Simple Sikuli example} % not related to gofigure...

@@

% ------------------------------------------------------------------------
\section{Example}

@@

% ------------------------------------------------------------------------
\section{Integration with CTest}

@@

# here we add a sikuli test
add_sikuli_test( ThunderbirdSikuliTest test.sikuli )
\end{verbatim}

@@

% ------------------------------------------------------------------------
\section{Current Limitation}

@@

% ------------------------------------------------------------------------
\section{Conclusion}

>>>>

GUI testing is a key aspect of software development. Having a well defined
testing protocol is very important in maintaining a productive flow, especially
on the eve of a new release. As the software becomes more complex, testing each
feature can be immensely time consuming. We collected a list of over 400
different GUI tests for the GoFigure2 software~\cite{GoFigure2:Website} which
involved endlessly repetitive clicking and checking. This task took around 5
hours to complete each time a new release was ready. And debugging would push
release dates back days or even weeks. We decided to tackle this problem by
utilizing a new scripting language called
Sikuli~\cite{Sikuli:Documentation,Sikuli:Website,Yeh:2009:Sikuli} that can
automate any visual operation. In this way we could write scripts to automate
the GUI testing. This cut the time to complete each test drastically.
Furthermore, we have integrated the automated tests with CTest. Therefore we
are able to run the collection of tests every night and find bugs as they
arise instead of the night before a new release. As a result, the rate of new
releases increased drastically.\\

The paper is organized as follows, first we will briefly introduce what is
Sikuli (in section~\ref{sec:WhatIsSikuli}) and show one simple example (in
section~\ref{sec:SimpleSikuliExample}). Then we will show a real test example
on GoFigure2 (in section~\ref{sec:GoFigure2Example}) and how to integrate
unit tests in CTest (in section~\ref{sec:IntegrationWithCTest}). Finally, we
will review the current limitation of Sikuli and this approach for GUI Testing
(in section~\ref{sec:Limitations}) and conclude (in
section~\ref{sec:Conclusion}).

@@

% Feel free to change section titles
\subsection{What is Sikuli?}
\label{sec:WhatIsSikuli}

@@

% ------------------------------------------------------------------------
\subsection{Simple Sikuli example} % not related to gofigure...
\label{sec:SimpleSikuliExample}

@@

% ------------------------------------------------------------------------
\section{Example}
\label{sec:GoFigure2Example}

@@

% ------------------------------------------------------------------------
\section{Integration with CTest}
\label{sec:IntegrationWithCTest}

@@

# here we add a sikuli test
add_sikuli_test( GoFigure2ToolbarTest toolbar.sikuli )
\end{verbatim}

@@

% ------------------------------------------------------------------------
\section{Current Limitations}
\label{sec:Limitations}

@@

% ------------------------------------------------------------------------
\section{Conclusion}
\label{sec:Conclusion}
